%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% Adaptation : Hyunggi Chang
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{kotex} % Enable Korean!

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\resumeSummary}[1]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1
    \end{tabular*}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      {\small #3} & {\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEmployment}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      \textit{\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProject}[3]{
  \item\small{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2
    \end{tabular*}#3\vspace{-2pt}
  }
}

\newcommand{\resumeResearch}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      \textit{\small#3} {\small #4 \vspace{-2pt}} & {\small #5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeTalk}[2]{
  \vspace{-1pt}\item\small{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
  }
}

\newcommand{\resumeSkills}[1]{
  \item\small{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1
    \end{tabular*}\vspace{-2pt}
  }
}

\newcommand{\resumeCommunity}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\gold}{★}
\newcommand{\bronze}{★}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeEmploymentListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeEmploymentListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Minjae Lee}} & Email : \href{mailto:leeminjae0129@gmail.com}{leeminjae0129@gmail.com} \\
  {} & Mobile : (+82) 10-7440-1538 \\
  {} & \href{https://scholar.google.com/citations?user=Ohcu4AwAAAAJ}{\textcolor{blue}{Scholar}} $|$ \href{https://orcid.org/0009-0005-2796-3207}{\textcolor{blue}{ORCID}} $|$ \href{https://www.linkedin.com/in/minjae-lee-9122bb252/}{\textcolor{blue}{LinkedIn}} $|$ \href{https://github.com/MinChoi0129}{\textcolor{blue}{GitHub}}
\end{tabular*}

%-----------Skills-----------------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeSkills{\textbf{Programming}: Python ($\geq$3.8), C++ ($\geq$17), C\#, JavaScript}
\resumeSkills{\textbf{Framework \& Library}: PyTorch, OpenCV, NumPy, Rerun, Open3D}
\resumeSkills{\textbf{CV / Robotics}: LiDAR Segmentation, Visual SLAM, Camera Calibration, Sensor Model Understanding}
\resumeSkills{\textbf{Mathematical Foundations}: Lie Groups \& Algebras, Linear Algebra, Probabilistic Modeling}
\resumeSkills{\textbf{Deep Learning}: 2D/3D Computer Vision, LLM, Training Methodology}
\resumeSkills{\textbf{Infrastructure \& Tools}: NVIDIA Jetson Device, Multi-GPU Linux Server Setup, Docker, Git/GitHub}
\resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSkills{LoRa-MOS: Range-Robust LiDAR Moving Object Segmentation (IEEE RA-L, under revision) & Feb. 2026 -- Present}
\resumeSkills{X-MOS: Cross-LiDAR Generalization Framework (ICRA 2026) & Aug. 2025 -- Jan. 2026}
\resumeSkills{SwiftMOS: Real-Time LiDAR Moving Object Segmentation (IEEE RA-L) & Jan. 2025 -- Jan. 2026}
\resumeSkills{J.A.R.V.I.S: LiDAR-Scan-based Digital Twin \& Gesture Interaction & Sep. 2024 -- Dec. 2024}
\resumeSkills{Finger-Pointing-based Small Robot Control (SIGGRAPH Asia 2024) & Mar. 2024 -- Dec. 2024}
\resumeSkills{{\footnotesize Shrunken Reality: SLAM-based Real-Time Real-World Context Augmentation (SIGGRAPH Asia)} & Jan. 2024 -- Dec. 2024}
\resumeSkills{SLAM-based Illegal Parking Detection System (SIGGRAPH Asia 2024) & Aug. 2023 -- Dec. 2024}
\resumeSkills{Low-Cost Augmented Reality Interaction (ETRI) & Jan. 2023 -- Dec. 2023}
\resumeSubHeadingListEnd

%-----------Languages-----------------
\section{Languages}
\resumeSubHeadingListStart
\resumeSkills{\textbf{Korean}: Native}
\resumeSkills{\textbf{English}: Conversational / Capable of Q\&A at international conferences / Speech contest award}
\resumeSubHeadingListEnd

%-----------Honors & Awards-----------------
\section{Honors \& Awards}
\resumeSubHeadingListStart
\resumeSkills{\textbf{Manufacturing AI Competition} -- Gyeongsang National University (\textbf{Excellence Award}) & May 2026}
\resumeSkills{\textbf{Young Pioneer Researcher Award} -- GNU Graduate School (\textbf{Excellence Award}) & May 2026}
\resumeSkills{\textbf{Glocal English Speech Contest} -- GNU Graduate School (\textbf{Excellence Award}) & May 2025}
\resumeSkills{\textbf{Gyeongsangnam-do Governor's Award} -- IT Engineering College Commencement (\textbf{Top of College}) & Feb. 2025}
\resumeSkills{\textbf{Capstone Design Competition} -- Gyeongsang National University (\textbf{Grand Prize}) & Dec. 2024}
\resumeSkills{\textbf{Naver 1784 School Revolution} -- Elementary AI Education, National 1st Place (\textbf{Grand Prize}) & Nov. 2023}
\resumeSkills{\textbf{Likelion Hackathon} -- Web Development, National 3rd Place (\textbf{Bronze}) & Aug. 2023}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Gyeongsang National University, Graduate School}{Jinju, South Korea}
{M.S. in Computer Science and Engineering (Expected) (GPA: 4.50/4.50)}{Mar. 2025 -- Present}
\resumeSubheading
{Gyeongsang National University}{Jinju, South Korea}
{B.S. in Computer Science (GPA: 4.32/4.50)}{Mar. 2020 -- Feb. 2025}
\resumeSubHeadingListEnd

%-----------Publications-----------------
\section{Publications}
\small First author: 9, Co-author: 9

\vspace{4pt}
\textbf{[International Journals]}
\resumeSubHeadingListStart
\resumeItem{\textbf{Lee, M.}, Kim, U., Kim, G. W., \& Lee, S. (2026). SwiftMOS: A Fast and Lightweight Moving Object Segmentation via Feature Flowing Direct View Transformation. \textit{IEEE Robotics and Automation Letters}.}
\resumeItem{\textbf{Lee, M.}, Lee, S., \& Seo, H. (2026). Enhancing Early Alzheimer's Disease Detection via Transfer Learning: From Big Structural MRI Datasets to Ethnically Distinct Small Cohorts. \textit{Applied Sciences}, 16(2), 1004.}
\resumeItem{Yeon, S., \textbf{Lee, M.}, Bae, J., \& Lee, S. (2026). Resolving Ambiguity in Pointing Gestures Using Contextual Reasoning from Large Language Models. \textit{Computer Modeling in Engineering \& Sciences}.}
\resumeSubHeadingListEnd

\textbf{[International Conferences]}
\resumeSubHeadingListStart
\resumeItem{\textbf{Lee, M.}, Ha, I., Choi, S. M., Kim, G. W., \& Lee, S. X-MOS: A Heterogeneous Cross-LiDAR Generalization Framework for Moving Object Segmentation. \textit{IEEE International Conference on Robotics and Automation (ICRA) 2026}.}
\resumeItem{\textbf{Lee, M.}, Choi, S. M., Kim, G. W., \& Lee, S. HBRB-BoW: A Retrained Bag-of-Words Vocabulary for ORB-SLAM via Hierarchical BRB-KMeans. \textit{IEEE International Conference on Robotics and Automation (ICRA) 2026} (Late-Breaking Results).}
\resumeItem{Kang, W., Kim, M., \textbf{Lee, M.}, Kim, U., Bae, J., Lee, S., Kim, G. W., \& Choi, S. M. Hierarchical Interests Modeling on Multiple Time Scales for Sequential Recommendation. \textit{Artificial Intelligence with Biased or Scarce Data Workshop at AAAI 2026}.}
\resumeItem{Kim, U., \textbf{Lee, M.}, Bae, J., Kim, M., Choi, S. M., \& Lee, S. Privacy-Preserving Argumentative Explanations. \textit{AAAI 2026}.}
\resumeItem{\textbf{Lee, M.}, Bae, J., Kim, U., Choi, S. M., \& Lee, S. Shrunken Reality: Augmenting Real-World Contexts in Real-Time on Realistic Miniature Dioramas. \textit{SIGGRAPH Asia 2024}.}
\resumeItem{Bae, J., \textbf{Lee, M.}, Kim, U., \& Lee, S. SLAM-Based Illegal Parking Detection System. \textit{SIGGRAPH Asia 2024}.}
\resumeItem{\textbf{Lee, M.}, Bae, J., Choi, S. M., \& Lee, S. Finger-Pointing Interface for Human Gesture Recognition Based on Real-Time Geometric Comprehension. \textit{SIGGRAPH Asia 2024}.}
\resumeSubHeadingListEnd

\textbf{[Domestic Journals]}
\resumeSubHeadingListStart
\resumeItem{\textbf{Lee, M.}, Bae, J., \& Lee, S. (2025). Watch My Wrist: Wrist Muscle Movement-based Hand Gesture Recognition for Out-of-Sight in Augmented Reality. \textit{The Journal of the Korean Institute of Information Technology}, 23(7), 167--170. (in Korean)}
\resumeItem{\textbf{Lee, M.}, Bae, J., Choi, S. M., \& Lee, S. (2024). Plane Detection and Projection-based Filter for Enhanced Moving Object Segmentation in 3D LiDAR Environments. \textit{The Journal of the Korean Institute of Information Technology}, 22(12), 19--27. (in Korean)}
\resumeSubHeadingListEnd

\textbf{[Domestic Conferences]}
\resumeSubHeadingListStart
\resumeItem{Ha, I., \textbf{Lee, M.}, \& Lee, S. Image-Processing-based Hand-Tremor Compensation Pointing System for Digital Presentation Environments. \textit{KIIT Fall Conference 2025}. (in Korean)}
\resumeItem{Yeon, S., \textbf{Lee, M.}, \& Lee, S. Low-Cost Mixed Reality (MR) System based on 3D Hand Tracking. \textit{KIIT Fall Conference 2024}. (in Korean)}
\resumeItem{Kim, U., \textbf{Lee, M.}, \& Lee, S. Multiplayer System Combining First-Person Mixed Reality and Real-Time Strategy. \textit{KIIT Fall Conference 2024}. (in Korean)}
\resumeItem{\textbf{Lee, M.}, Bae, J., \& Lee, S. Plane-Detection-Filter-based Moving Object Segmentation in 3D LiDAR Environments. \textit{KIIT Fall Conference 2024}. (in Korean)}
\resumeItem{Kim, U., Bae, J., \textbf{Lee, M.}, \& Lee, S. Explainable Facial Beauty Prediction Model. \textit{KIIT Fall Conference 2023}. (in Korean)}
\resumeItem{Bae, J., \textbf{Lee, M.}, Kim, U., \& Lee, S. SLAM-based Illegal Parking Detection System. \textit{KIIT Fall Conference 2023}. (in Korean)}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
